\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-06 paper/draft.tex
Add shadowing figure
Add example

\subsection{Transformation}
\label{two}

@@

>>>>

\begin{figure}[t]
\centering 
\includegraphics[width=0.45\textwidth]{./figs/lya_shadowing.pdf}
\caption{
  \textbf{Shadowing segments.}
  \textmd{
  Cross-module variable name resolution (left) augmented with \sys (green boxes), which interjects non-bypassable steps resolving to \sys-augmented values (right-top: implicit module imports; right-bottom: explicit import).
  }
  \vspace{-4mm}
}
\label{fig:shadowing}
\end{figure}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.99\textwidth]{./figs/lya_ex.pdf}
\vspace{-2mm}
\caption{
  \textbf{Example transformations.}
   Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
}
\label{fig:tx2}
\vspace{-2mm}
\end{figure*}
